### 2016-02-19 paper.tex
Title case

    \caption{{\bf RM2 near-wake Turbulence Kinetic Energy.} Turbulence kinetic
        energy in the RM2's near-wake (looking upstream) at 1 m downstream
        ($x/D=0.93$), $U_\infty=1.0$ m/s, and $\lambda=3.1$. Solid black lines
        indicate turbine frontal area.}

>>>>

    \caption{{\bf RM2 Near-Wake Turbulence Kinetic Energy.} Turbulence kinetic
        energy in the RM2's near-wake (looking upstream) at 1 m downstream
        ($x/D=0.93$), $U_\infty=1.0$ m/s, and $\lambda=3.1$. Solid black lines
        indicate turbine frontal area.}
